Accessing biological data with semantic web technologies

### 2013-12-31 article.tex
Fixed the KI affiliation

\noindent
$^1$ Department of Bioinformatics - BiGCaT, NUTRIM, Maastricht University, Maastricht, The Netherlands \\
$^2$ Department of Molecular Toxicology, IMM, Karolinska Institutet, Stockholm, Sweden

>>>>

\noindent
$^1$ Department of Bioinformatics - BiGCaT, NUTRIM, Maastricht University, Maastricht, The Netherlands \\
$^2$ Division of Molecular Toxicology, IMM, Karolinska Institutet, Stockholm, Sweden
